|

### 2020-11-24 paper/v1/broadband.speed.covid.Rmd
changes after we spoke on 24/11

For this paper we utilise the third category of time series clustering methods
known as shape-based approaches. The main idea is to match any two sperate time
series based on the similarity of their shapes through the calculation of
distances among these two shapes.

@sardatime
Ideally, all members of the same cluster are similar to each other, but are as
dissimilar as possible from objects in a different cluster.

Time-series is a common type of dynamic data that naturally arises in many different scenarios,
such as stock data, medical data, and machine monitoring, just to name a few (Aghabozorgi et al.,
2015; Aggarwal and Reddy, 2013). They pose some challenging issues due to the large size and high
dimensionality commonly associated with time-series (Aghabozorgi et al., 2015). In this context,
dimensionality of a series is related to time, and it can be understood as the length of the series.

the data and how the underlying grouping is performed. One classification depends on whether the
whole series, a subsequence, or individual time points are to be clustered. On the other hand, the
clustering itself may be shape-based, feature-based, or model-based.

In the context of shape-based time-series clustering, it is common to utilize the Dynamic Time
Warping (DTW) distance as dissimilarity measure (Aghabozorgi et al., 2015). The calculation of the
DTW distance involves a dynamic programming algorithm that tries to find the optimum warping
path between two series under certain constraints

>>>>

For this paper we utilise the third category of time series clustering methods
known as shape-based approaches. The main idea is to match any two sperate time
series based on the similarity of their shapes through the calculation of
distances among these two shapes. Such approached are better equipped to capture
similarities between short length time series [@aghabozorgi2015time].
This approach serves best this paper because (i) we aim to identify clusters of
UK local authorities with similar temporal signatures -- i.e. shapes -- of
experienced internet speeds and (ii) the length of our time series is short
(**see also discussion in Section XX**).

Other important dimensions regarding time series clustering are related with the
clustering algorithm. Similar to clustering of cross-sectional data, we can employ
partitioning algorithms, which lead to non-overlapping clusters, hierarchical
clustering, which result to a hierarchy of clusters and fuzzy algorithms, which
create overlapping clusters [@sardatime]. Because of the simplicity of the
implementation and the interpretability of the results, we utilise here
partitioning clustering based on the widely *k-Means* algorithm. This is an iterative
algorithm, which begins with defining the desired number of clusters *k*. Then,
each observation is randomly assigned to a cluster from the $[1,k]$ space. This
is the initial cluster assignment, which is followed by iterations in order to
minimise the distance between the centroids of the clusters and the observations
assigned to these clusters [@james2013introduction].

There are a number of differences between the above described application of
*k-Means* for cross-sectional data and its application for times series data.

k-Meidoids
distance between points in time series
dt

comparison with density-based clustering DBSCAN [187]
where a cluster is expanded if its neighbours are dense.

- evaluation
- standardised

@sardatime
In the context of shape-based time-series clustering, it is common to utilize the Dynamic Time
Warping (DTW) distance as dissimilarity measure (Aghabozorgi et al., 2015). The calculation of the
DTW distance involves a dynamic programming algorithm that tries to find the optimum warping
path between two series under certain constraints
